Output Summary

### 2023-07-06 03-post-process/output-plots-children/04-egg-to-parr-surv.Rmd
Updates to new content
Misc. bugs, typos, optimizations missed previously

  # add a time series mean
  mn = mean(est["mean",])
  segments(min(all_yrs[ts_yrs]), mn, max(all_yrs[ts_yrs]), mn, lty = 2, lwd = 2, col = main_cols["model"])
}

>>>>

  # add a time series mean
  mn = mean(est["mean",])/1000
  segments(min(all_yrs[ts_yrs]), mn, max(all_yrs[ts_yrs]), mn, lty = 2, lwd = 2, col = main_cols["model"])
}
